Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-14 ICML-submission/figures/pizza-slice.tex
Small fixes

  \coordinate (C) at (120:3);
  \coordinate (C1) at ($(120:3) + (0.75, 0.43301270189221932338)$);
  \coordinate (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);
  \draw[<->, >=latex', ultra thick] (C1) -- (C);
  \draw[<->, >=latex', ultra thick] (C2) -- (C);
  \draw ($0.5*(C1) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
  \draw ($0.5*(C2) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};

  \coordinate (D) at (240:3);
  \coordinate (D1) at ($(240:3) + (-0.75, 0.43301270189221932338)$);
  \coordinate (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
  \draw[<->, >=latex', ultra thick] (D1) -- (D);
  \draw[<->, >=latex', ultra thick] (D2) -- (D);
  \draw ($0.5*(D1) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};
  \draw ($0.5*(D2) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};

>>>>

  \coordinate (C) at (120:3);
  \coordinate (C1) at ($(120:3) + (0.75, 0.43301270189221932338)$);
  \coordinate (C2) at ($(120:3) - (0.75, 0.43301270189221932338)$);

  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (C1) -- (C);
  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (C2) -- (C);
  \draw ($0.5*(C1) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};
  \draw ($0.5*(C2) + 0.5*(C)$) node[above, xshift=-1mm] {$\gamma$};

  \coordinate (D) at (240:3);
  \coordinate (D1) at ($(240:3) + (-0.75, 0.43301270189221932338)$);
  \coordinate (D2) at ($(240:3) - (-0.75, 0.43301270189221932338)$);
  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (D1) -- (D);
  \draw [<->, >=latex, decoration={markings,mark=at position 1 with {\arrow[scale=0.5]{>}}},postaction={decorate}] (D2) -- (D);
  \draw ($0.5*(D1) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};
  \draw ($0.5*(D2) + 0.5*(D)$) node[below, xshift=-1mm] {$\gamma$};
